The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-10 analysis/paper/paper.qmd
Update analysis/paper/paper.qmd

vizDataFrameWithYear <- melt(cbind(data.frame(topic_prop_per_year), 
                           document = factor(rownames(topic_prop_per_year))), 
                     variable.name = "topic", id.vars = "document") |> 
    left_join(select(emu_theses, title, "year" = graduation_year), by = c("document" = "title"))

>>>>

# TODO change to pivot_longer
vizDataFrameWithYear <- melt(cbind(data.frame(topic_prop_per_year), 
                           document = factor(rownames(topic_prop_per_year))), 
                     variable.name = "topic", id.vars = "document") |> 
    left_join(select(emu_theses, title, "year" = graduation_year), by = c("document" = "title"))
